Designing Types for R, Empirically

### 2020-05-16 paper/main.tex
types in types out

@@

type `emulator::cprod` <class<`matrix`> | double[], class<`matrix`> | double[]> => class<`matrix`>;

type `lava::lava.options` <...> => list<double | character[]>;

type `coin::\%GE\%` <class<`matrix`> | class<`matrix`, `pvalue`> | double[], double[] | class<`matrix`, `pvalue`>> => (class<`matrix`> | logical[]);

type `emplik::gradf` <class<`matrix`>, double[], double[]> => double[];

type `fields::rdist` <class<`data.frame`> | class<`matrix`> | double[], class<`data.frame`> | class<`matrix`> | null | double[], logical> => (class<`matrix`> | class<`dist`>);

type `stabledist::x.exp.m.x` <double[]> => double[];

type `pkgload::compact` <list<any>> => list<any>;

type `bbmle::relist2` <double[], double[] | list<any>> => list<any>;

type `stabledist::cospi2` <double[]> => double[];
type `stabledist::tanpi2` <double[]> => double[];

type `neuralnet::relist` <double[], class<`array`> | integer[], class<`array`> | integer[]> => list<class<`matrix`>>;
type `neuralnet::calculate.gradients` <any, integer, list<class<`matrix`>>, any, class<`matrix`>, double, logical> => double[];

>>>>

type `dplyr::group\_indices` <class<`data.frame`>, ...> => integer[];

type `stabledist::cospi2` <double[]> => double[];

@@

type `openssl::decrypt\_envelope` <raw[], raw[], raw[], class<`key`, `rsa`>, any> => raw[];

dbplyr:type `set\_win\_current\_group` <null | character[]> => (character[] | null);

type `sha256` <raw[], null | raw[]> => raw[];

type `initparam` <? double, any, any, any, character, character, logical, double[], double[], any> => double[];
